---
title: "Analysis of HR Data"
author: "Agustin Gonzalez-Quel"
date: "May 20th, 2017"
runtime: shiny
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Human Resources {.smaller}

The work included in this presentation is based on a Datased from Kaggle <https://www.kaggle.com> by Ludovic Benistant, released under  <https://creativecommons.org/licenses/by-sa/4.0/> License.

The Dataset includes anonymised information on employees, including the following fields:

- Satisfaction Level,
- Last Evaluation
- Number of projects
- Average monthy hours
- Time spent in the company (years)
- Salary level (High, Medium, Low)

Data is included in the file "HR_comma_sep.csv" provided.

## Loading the data {.smaller}

We read the file into a data frame. Let's have a look

```{r, echo = TRUE, warning = FALSE, message=FALSE}
library(ggplot2)
hr<- read.csv("HR_comma_sep.csv")
head(hr)
```

In the Shiny presentation, we include an Slider for the user to select a number of employees to display: between 100 and 2000.

## Human Resources {.smaller}

What we want to explore is the relationship between worked hours and satisfaction of the employee using a shiny applicacion.

This application will allow the user to select a number of employees to be displayed in a plot showing the above mentioned relationship.

Using the slider, the user will visually check how the distribution evolves with the number of employees.

## The Shiny App {.smaller}

```{r echo = FALSE}
    sliderInput("employees", "Number of Employees:", 
                 min = 100, max = 2000, value = 200)
```

```{r echo = FALSE}
renderPlot({
  hr <- hr[0:input$employees,]
  qplot(data = hr,
          main = "Worked hours vs Satisfaction level",
          x = hr$average_montly_hours, 
          y = hr$satisfaction_level,
          xlab = "Monthly worked hours",
          ylab = "Satisfaction level",
          color = hr$salary
          ) + labs(color = "Salary level")
  
})
```

## Future work

It will be interesting to further explore this data, including the information of years spent in the company.

We will also use predictive modelling to find out any predictability.
